Supplementary Materials

### 2024-10-19 pilot-publication/supplementary-materials.Rmd
Add right tables to supplementary materials

---
title: Supplementary Materials
subtitle: "Effect of Trauma Life Support Training on Patient Outcomes: A Pilot Cluster Randomised Trial"
output:
    bookdown::word_document2:
      number_sections: false
      reference_docx: "reference.docx"
---

@@

```{r, child = "outcome-tables.Rmd"}
```

>>>>

---
title: Supplementary Materials
subtitle: "Effect of Trauma Life Support Training on Patient Outcomes: A Pilot Cluster Randomised Trial"
output:
    bookdown::word_document2:
      number_sections: false
      reference_docx: "reference.docx"
      toc: true
---

@@

```{r, child = "supplementary-outcome-tables.Rmd"}
```
